### 2022-05-17 manuscript.Rmd
Improve formatting of frequentist statistics

    # Add difference between condition means
    mean_diff = case_when(
      !is.na(mean_diff) ~ mean_diff,
      TRUE ~ mean_novel - mean_familiar
    ),
    # Add d_z from paired-samples t-test of condition means (Rosenthal, 1991)
    d_z_t = t / sqrt(sample_size),
    # Add d_z from ANOVA F-statistic via conversion to a t-statistic
    d_z_f = sqrt(f) / sqrt(sample_size) * sign_f,
    # Add d_z from mean and standard deviation of the difference
    d_z_diff = mean_diff / sd_diff,
    # Add d_av from mean difference and standard deviations
    # See http://dx.doi.org/10.20982/tqmp.14.4.p242
    sd_av = sqrt((sd_novel^2 + sd_familiar^2) / 2),
    d_av = mean_diff / sd_av,
    # Add d from one-sample t-test of novelty preference scores
    d_nov_pref = (nov_pref - 0.5) / sd_nov_pref,

@@

    # Re-code non-significant F-statistics as an effect size of d = 0
    f = as.numeric(f),
    f_assumed = ifelse(is.nan(f), 0, f),

@@

    # Add d from ANOVA F-statistic via conversion to a t-statistic
    d_f = sqrt(f_assumed) * sqrt(1 / female_n + 1 / male_n),

@@

We inspected funnel plots and performed Egger regression tests to examine the possibility of publication bias in the literature included here. For the meta-analysis of mental rotation performance (Fig.\ \@ref(fig:fig3)a), we observed a slight asymmetry in the funnel plot, indicating a small publication bias. This was confirmed by an Egger regression test that showed a reliable association between effect sizes and their corresponding standard errors, $b = `r coef(egger_meta$fit)["Xsei"]`$, $t(`r egger_meta$dfs`) = `r egger_meta$zval`$, $p = `r print_p(egger_meta$pval)`$, 95% confidence interval (CI) [`r egger_ci_meta["2.5 %"]`, `r egger_ci_meta["97.5 %"]`] (two-sided test). Nevertheless, a jackknife (leave-one-out analysis) confirmed that the current results are robust to the effects of individual outlier studies (Supplementary Table\ \@ref(tab:tabs3)). For the meta-analysis of gender differences in mental rotation performance (Fig.\ \@ref(fig:fig3)b), the asymmetry in the funnel plot was less pronounced and the slope of the Egger regression test was not statistically significant, $b = `r coef(egger_gender$fit)["Xsei"]`$, $t(`r egger_gender$dfs`) = `r egger_gender$zval`$, $p = `r print_p(egger_gender$pval)`$, 95% confidence interval (CI) [`r egger_ci_gender["2.5 %"]`, `r egger_ci_gender["97.5 %"]`] (two-sided test).

@@

Two independent raters read the abstract and, if necessary, relevant sections of the full text to check if an article fulfilled the inclusion criteria. Interrater agreement for the binary decision to include versus exclude an article was `r print_perc(irr_bin_perc)` ($\kappa_w$ [Cohen's weighted kappa] $= `r irr_bin_kappa_w$estimate`$, 95% CI [`r irr_bin_kappa_w$lower`, `r irr_bin_kappa_w$upper`]). Interrater agreement for the specific eligibility criteria was `r print_perc(irr_code_perc)` ($\kappa_w$ $= `r irr_code_kappa_w$estimate`$, 95% CI [`r irr_code_kappa_w$lower`, `r print_num(irr_code_kappa_w$upper)`]). Cases where the two ratings diverged were resolved via discussion among all raters until a consensus was reached. One article [@mash2007] was excluded because the authors used a unique mental rotation paradigm that was not comparable to the paradigm used in the other articles. Another article [@pedrett2020] was excluded because the average age of the infants studied (`r print_num(descs_pedrett2020$age_months, 1)` months) was almost twice as high as the average age of the next article (`r print_num(descs_pedrett2020$next_largest_age_months, 1)` months; $z = `r descs_pedrett2020$z`$ compared to all articles). We therefore decided to narrow our analysis from the first 3 years of life to the first 16 months of life. This procedure led to a total of `r descriptives$n_articles` articles being included in the meta-analysis (Fig.\ \@ref(fig:fig4)).

>>>>

    # Add difference between condition means
    mean_diff = case_when(
      !is.na(mean_diff) ~ mean_diff,
      TRUE ~ mean_novel - mean_familiar
    ),
    # Add d_z from paired-samples t-test of condition means (Rosenthal, 1991)
    d_z_t = t / sqrt(sample_size),
    # Add d_z from ANOVA F statistic via conversion to a t statistic
    d_z_f = sqrt(f) / sqrt(sample_size) * sign_f,
    # Add d_z from mean and standard deviation of the difference
    d_z_diff = mean_diff / sd_diff,
    # Add d_av from mean difference and standard deviations
    # See http://dx.doi.org/10.20982/tqmp.14.4.p242
    sd_av = sqrt((sd_novel^2 + sd_familiar^2) / 2),
    d_av = mean_diff / sd_av,
    # Add d from one-sample t-test of novelty preference scores
    d_nov_pref = (nov_pref - 0.5) / sd_nov_pref,

@@

    # Re-code non-significant F statistics as an effect size of d = 0
    f = as.numeric(f),
    f_assumed = ifelse(is.nan(f), 0, f),

@@

    # Add d from ANOVA F statistic via conversion to a t statistic
    d_f = sqrt(f_assumed) * sqrt(1 / female_n + 1 / male_n),

@@

We inspected funnel plots and performed Egger regression tests to examine the possibility of publication bias in the literature included here. For the meta-analysis of mental rotation performance (Fig.\ \@ref(fig:fig3)a), we observed a slight asymmetry in the funnel plot, indicating a small publication bias. This was confirmed by an Egger regression test that showed a reliable association between effect sizes and their corresponding standard errors, $b = `r coef(egger_meta$fit)["Xsei"]`$, $t(`r egger_meta$dfs`) = `r egger_meta$zval`$, $P = `r print_num(egger_meta$pval, digits = 3)`$, 95% confidence interval (CI) [`r egger_ci_meta["2.5 %"]`, `r egger_ci_meta["97.5 %"]`] (two-sided test). Nevertheless, a jackknife (leave-one-out analysis) confirmed that the current results are robust to the effects of individual outlier studies (Supplementary Table\ \@ref(tab:tabs3)). For the meta-analysis of gender differences in mental rotation performance (Fig.\ \@ref(fig:fig3)b), the asymmetry in the funnel plot was less pronounced and the slope of the Egger regression test was not statistically significant, $b = `r coef(egger_gender$fit)["Xsei"]`$, $t(`r egger_gender$dfs`) = `r egger_gender$zval`$, $P = `r print_num(egger_gender$pval, digits = 3)`$, 95% confidence interval (CI) [`r egger_ci_gender["2.5 %"]`, `r egger_ci_gender["97.5 %"]`] (two-sided test).

@@

Two independent raters read the abstract and, if necessary, relevant sections of the full text to check if an article fulfilled the inclusion criteria. Interrater agreement for the binary decision to include versus exclude an article was `r print_perc(irr_bin_perc)` ($\kappa_w$ [Cohen's weighted kappa] $= `r irr_bin_kappa_w$estimate`$, 95% CI [`r irr_bin_kappa_w$lower`, `r irr_bin_kappa_w$upper`]). Interrater agreement for the specific eligibility criteria was `r print_perc(irr_code_perc)` ($\kappa_w$ $= `r irr_code_kappa_w$estimate`$, 95% CI [`r irr_code_kappa_w$lower`, `r print_num(irr_code_kappa_w$upper)`]). Cases where the two ratings diverged were resolved via discussion among all raters until a consensus was reached. One article [@mash2007] was excluded because the authors used a unique mental rotation paradigm that was not comparable to the paradigm used in the other articles. Another article [@pedrett2020] was excluded because the average age of the infants studied (`r print_num(descs_pedrett2020$age_months, digits = 1)` months) was almost twice as high as the average age of the next article (`r print_num(descs_pedrett2020$next_largest_age_months, digits = 1)` months; $Z = `r descs_pedrett2020$z`$ compared to all articles). We therefore decided to narrow our analysis from the first 3 years of life to the first 16 months of life. This procedure led to a total of `r descriptives$n_articles` articles being included in the meta-analysis (Fig.\ \@ref(fig:figs2)).

### 2022-05-17 supplement.Rmd
Merge split reference sections again
Improve formatting of frequentist statistics

<!-- Restart numbering of figures, tables, equations, and pages -->
\renewcommand{\thefigure}{\arabic{figure}}
\renewcommand{\thetable}{\arabic{table}}
\renewcommand{\theequation}{\arabic{table}}
\setcounter{figure}{0}
\setcounter{table}{0}
\setcounter{equation}{0}
\setcounter{page}{1}

@@

In our next step, we used selection models to approximate the process by which experiments got selected into the meta-analysis. These models were based on the assumption that experiments yielding significant effects (i.e., small *p*-values) are more likely to get published. Specifically, we ran one selection model assuming a weight function with fixed *p*-value cutoffs [@vevea1995] at *p* = .01, *p* = .05, and *p* = .30. Additionally, we ran multiple models with a priori selection functions assuming biases of varying severity [@vevea2005]. These analyses  revealed that our results are robust to small to medium publication bias (Supplementary Tables\ \@ref(tab:tabs10) and \@ref(tab:tabs11)).

@@

+----------------------------------------------------------------+---------------------------------------------------------------------------------------------+
| \ \ Available statistics                                       | Conversion to standardized mean difference (Hedges' $g$)                                    |
+================================================================+=============================================================================================+
| \ \ (1\) Cohen's $d$ and sample size                           | ${df}=2(n-1)$;\quad                                                                         |
| [@goulet-pelletier2018; @hedges1985]                           | $J({df})=\frac{\Gamma(\frac{1}{2}{df})}{\sqrt{\frac{{df}}{2}}\Gamma(\frac{1}{2}({df}-1))}$; |
|                                                                | \quad $g_\text{rotation}=d\cdot{J}({df})$                                                   |
+----------------------------------------------------------------+---------------------------------------------------------------------------------------------+
| \ \ (2\) $t$-statistic and sample size [@rosenthal1991]        | $d=\frac{t}{\sqrt{n}}$;\quad then (1)                                                       |
+----------------------------------------------------------------+---------------------------------------------------------------------------------------------+
| \ \ (3\) $F$-statistic and sample size [@lakens2013]           | $t=\sqrt{f}$;\quad then (2\)                                                                |
+----------------------------------------------------------------+---------------------------------------------------------------------------------------------+
| \ \ (4\) Mean difference between conditions [@lakens2013]      | $d=\frac{m_\text{diff}}{{SD}_\text{diff}}$;\quad then (1)                                   |
+----------------------------------------------------------------+---------------------------------------------------------------------------------------------+
| \ \ (5\) Mean looking time and ${SD}$ per condition            | ${SD}_\text{av}=\sqrt{\frac{{SD}_\text{novel}^2+{SD}_\text{familiar}^2}{2}}$;\quad          |
| [@cumming2012]                                                 | $d=\frac{m_\text{novel}-m_\text{familiar}}{{SD}_\text{av}}$;\quad then (1)                  |
+----------------------------------------------------------------+---------------------------------------------------------------------------------------------+
| \ \ (6\) Mean novelty preference score [@lakens2013]           | $d=\frac{m_\text{pref}}{{SD}_\text{pref}}$;\quad then (1)                                   |
+----------------------------------------------------------------+---------------------------------------------------------------------------------------------+

@@

+----------------------------------------+--------------------------------------------------------------------------------------------------+
| \ \ Available statistics               | Conversion to standardized mean difference (Hedges' $g$)                                         |
+========================================+==================================================================================================+
| \ \ (1\) Cohen's $d$ and group sizes   | ${df}=n_\text{female}+n_\text{male}-1$; \quad                                                    |
| [@goulet-pelletier2018; @hedges1985]   | $J({df})=\frac{\Gamma(\frac{1}{2}{df})}{\sqrt{\frac{{df}}{2}}\Gamma(\frac{1}{2}({df}-1))}$;\quad |
|                                        | $g_\text{gender}=d\cdot{J({df})}$                                                                |
+----------------------------------------+--------------------------------------------------------------------------------------------------+
| \ \ (2\) $t$-statistic and group sizes | $d=t\sqrt{\frac{1}{n_\text{female}}+\frac{1}{n_\text{male}}}$;\quad then (1)                     |
| [@lakens2013]                          |                                                                                                  |
+----------------------------------------+--------------------------------------------------------------------------------------------------+
| \ \ (3\) $F$-statistic and group sizes | $t=\sqrt{f}$;\quad then (2\)                                                                     |
| [@lakens2013]                          |                                                                                                  |
+----------------------------------------+--------------------------------------------------------------------------------------------------+
| \ \ (4\) Mean differences between\     | ${SD}_\text{pooled}=\sqrt{\frac{(n_\text{female}-1){SD}_\text{female}^2                          |
| \ \ conditions or preference scores    | +(n_\text{male}-1){SD}_\text{male}^2}{df}}$;\quad                                                |
| [@lakens2013]                          | $d=\frac{m_\text{female}-m_\text{male}}{{SD}_\text{pooled}}$;\quad then (1)                      |
+----------------------------------------+--------------------------------------------------------------------------------------------------+

>>>>

<!-- Restart numbering of figures and tables -->
\renewcommand{\thefigure}{\arabic{figure}}
\renewcommand{\thetable}{\arabic{table}}
\setcounter{figure}{0}
\setcounter{table}{0}

<!-- Restart page and line numbers -->
\setcounter{page}{1}
\resetlinenumber
\linenumbers

@@

In our next step, we used selection models to approximate the process by which experiments got selected into the meta-analysis. These models were based on the assumption that experiments yielding significant effects (i.e., small $P$ values) are more likely to get published. Specifically, we ran one selection model assuming a weight function with fixed $P$ value cutoffs [@vevea1995] at $P$ = .01, $P$ = .05, and $P$ = .30. Additionally, we ran multiple models with a priori selection functions assuming biases of varying severity [@vevea2005]. These analyses  revealed that our results are robust to small to medium publication bias (Supplementary Tables\ \@ref(tab:tabs10) and \@ref(tab:tabs11)).

@@

+----------------------------------------------------------------+---------------------------------------------------------------------------------------------+
| \ \ Available statistics                                       | Conversion to standardized mean difference (Hedges' $g$)                                    |
+================================================================+=============================================================================================+
| \ \ (1\) Cohen's $d$ and sample size                           | ${df}=2(n-1)$;\quad                                                                         |
| [@goulet-pelletier2018; @hedges1985]                           | $J({df})=\frac{\Gamma(\frac{1}{2}{df})}{\sqrt{\frac{{df}}{2}}\Gamma(\frac{1}{2}({df}-1))}$; |
|                                                                | \quad $g_\text{rotation}=d\cdot{J}({df})$                                                   |
+----------------------------------------------------------------+---------------------------------------------------------------------------------------------+
| \ \ (2\) $t$ statistic and sample size [@rosenthal1991]        | $d=\frac{t}{\sqrt{n}}$;\quad then (1)                                                       |
+----------------------------------------------------------------+---------------------------------------------------------------------------------------------+
| \ \ (3\) $F$ statistic and sample size [@lakens2013]           | $t=\sqrt{f}$;\quad then (2\)                                                                |
+----------------------------------------------------------------+---------------------------------------------------------------------------------------------+
| \ \ (4\) Mean difference between conditions [@lakens2013]      | $d=\frac{m_\text{diff}}{{SD}_\text{diff}}$;\quad then (1)                                   |
+----------------------------------------------------------------+---------------------------------------------------------------------------------------------+
| \ \ (5\) Mean looking time and ${SD}$ per condition            | ${SD}_\text{av}=\sqrt{\frac{{SD}_\text{novel}^2+{SD}_\text{familiar}^2}{2}}$;\quad          |
| [@cumming2012]                                                 | $d=\frac{m_\text{novel}-m_\text{familiar}}{{SD}_\text{av}}$;\quad then (1)                  |
+----------------------------------------------------------------+---------------------------------------------------------------------------------------------+
| \ \ (6\) Mean novelty preference score [@lakens2013]           | $d=\frac{m_\text{pref}}{{SD}_\text{pref}}$;\quad then (1)                                   |
+----------------------------------------------------------------+---------------------------------------------------------------------------------------------+

@@

+----------------------------------------+--------------------------------------------------------------------------------------------------+
| \ \ Available statistics               | Conversion to standardized mean difference (Hedges' $g$)                                         |
+========================================+==================================================================================================+
| \ \ (1\) Cohen's $d$ and group sizes   | ${df}=n_\text{female}+n_\text{male}-1$; \quad                                                    |
| [@goulet-pelletier2018; @hedges1985]   | $J({df})=\frac{\Gamma(\frac{1}{2}{df})}{\sqrt{\frac{{df}}{2}}\Gamma(\frac{1}{2}({df}-1))}$;\quad |
|                                        | $g_\text{gender}=d\cdot{J({df})}$                                                                |
+----------------------------------------+--------------------------------------------------------------------------------------------------+
| \ \ (2\) $t$ statistic and group sizes | $d=t\sqrt{\frac{1}{n_\text{female}}+\frac{1}{n_\text{male}}}$;\quad then (1)                     |
| [@lakens2013]                          |                                                                                                  |
+----------------------------------------+--------------------------------------------------------------------------------------------------+
| \ \ (3\) $F$ statistic and group sizes | $t=\sqrt{f}$;\quad then (2\)                                                                     |
| [@lakens2013]                          |                                                                                                  |
+----------------------------------------+--------------------------------------------------------------------------------------------------+
| \ \ (4\) Mean differences between\     | ${SD}_\text{pooled}=\sqrt{\frac{(n_\text{female}-1){SD}_\text{female}^2                          |
| \ \ conditions or preference scores    | +(n_\text{male}-1){SD}_\text{male}^2}{df}}$;\quad                                                |
| [@lakens2013]                          | $d=\frac{m_\text{female}-m_\text{male}}{{SD}_\text{pooled}}$;\quad then (1)                      |
+----------------------------------------+--------------------------------------------------------------------------------------------------+
